A survey of HTTP caching options on the open Semantic Web

### 2015-01-16 sanity/paper1.tex
Clear cuts
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@996 43ef1190-90fd-4dd7-a769-d0121f02b80e

In \cite{ldf1}, it was asserted that SPARQL query caching is only
possible on a per-query basis, but future research should challenge
this assumption. With this in mind, if reasoning is not involved, we
note that ontologies are not relevant to query answering since they
usually occur in bound terms. It is interesting to understand caching
when this is not the case. Moreover, many ontologies are maintained by
a small group of humans and change seldomly.\todo{not particularly clear}

@@

Caching may also be prohibited by setting a non-positive freshness
lifetime. Common practice is to set the \httph{Expires} header to a
date far back in time, which has also been done in large parts of the
present dataset. For the following, we have set any non-positive
lifetime to 0, as that is semantically equivalent. With that, we
obtain the summary statistics in Table~\ref{tab:summaryhard}.

\begin{table}[ht]
\begin{center}
\caption{Summary statistics for standards-compliant freshness lifetime}\label{tab:summaryhard}
\begin{tabular}{lr}
Min.   &       0   \\ 
1st Qu.&       0   \\ 
Median &     600   \\ 
Mean   &  583003   \\ 
3rd Qu.&  172800   \\ 
Max.   & 52702521   \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{2.3cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline

>>>>

@@

Caching may also be prohibited by setting a non-positive freshness
lifetime. Common practice is to set the \httph{Expires} header to a
date far back in time, which has also been done in large parts of the
present dataset. For the following, we have set any non-positive
lifetime to 0, as that is semantically equivalent.

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{1.4cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline
